01_limma_all

### 2019-05-16 analysis/01_limma_all.Rmd
no large file or long output in md
removeing df outputs with head()
removed about output table

# find and print data
names(parentalobject)
head(countData)
head(parentalobject$counts)
head(parentalobject$pseudo.counts)

@@

#  perform likelihood ratio test and thresholded testing
fit <- glmFit( parentalobject, parentaldesign, robust=T)
tr <- glmTreat(fit, lfc = 1)
topTags(tr)
tr$table
```

>>>>

# find and print data
names(parentalobject)
#head(countData)
#head(parentalobject$counts)
#head(parentalobject$pseudo.counts)

@@

#  perform likelihood ratio test and thresholded testing
fit <- glmFit( parentalobject, parentaldesign, robust=T)
tr <- glmTreat(fit, lfc = 1)
topTags(tr)
#tr$table
```
